Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
added algorithm figures

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{svg}

@@

Insert the figure 4 from the paper!

This figure, included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.  
The subfigures in this diagram explain on a high level the different steps the interface layer takes when solving a problem.  
The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.  
Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.  
There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.  
This triggers the behavior discussed earlier, where the state is updated for the task planner.  
Subfigure e shows the new task plan after replanning occurs.  
After this, the interface layer will repeat the process of attempting to refine this new plan.  
Subfigure f shows an alternative option, where the blocking object is determined to be the table, which is not movable.  
Then, the state is updated as before and the task planner is called, but no solution is found, so backtracking occurs.

\subsubsection{Algorithm Improvements}

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

@@

Include algorithm block 1 from paper

@@

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

@@

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|}
\hline
Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
Horizontal Line & 3 & 12 & 3 & 1 & .023\\
& 5 & 24 & 4 & 1 & .028\\
& 7 & 36 & 4 & 1 & .029\\
& 9 & 48 & 4 & 1 & .029\\
& 11 & 60 & 4 & 1 & .034\\
& 13 & 72 & 4 & 1 & .037\\
\hline
Vertical Line & 3 & 12 & 4 & 1 & .024\\
& 5 & 24 & 4 & 1 & .027\\
& 7 & 36 & 4 & 1 & .028\\
& 9 & 48 & 4 & 1 & .028\\
& 11 & 60 & 4 & 1 & .037\\
& 13 & 72 & 4 & 1 & .036\\ 
\hline
X & 5 & 8 & 2 & 1 & .026\\
& 9 & 16 & 2 & 1 & .034\\
& 13 & 24 & 2 & 1 & .036\\
& 17 & 32 & 2 & 1 & .047\\
& 21 & 40 & 2 & 1 & .066\\
& 25 & 48 & 2 & 1 & .079\\ 
\hline
Cross & 5 & 20 & 39 & 3 & .16\\
& 9 & 44 & 50 & 2 & .20\\
& 13 & 68 & 59 & 2 & .23\\
& 17 & 92 & 71 & 3 & .26\\
& 21 & 116 & 78 & 3 & .31\\
& 25 & 140 & 77 & 3 & .39\\ 
\hline
Square & 9 & 56 & 54 & 2 & .16\\
& 25 & 176 & 294 & 6 & 1.06\\
& 49 & 360 & 818 & 10 & 5.07\\
& 81 & 608 & 3177 & 24 & 34.68\\
& 121 & 920 & 3681 & 22 & 87.06\\
& 169 & 1296 & 14216 & 57 & 518.61\\ 
\hline

>>>>

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{svg}
\usepackage{caption}
\usepackage{subfig}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/figure4.png}
\caption{Illustration of the interface layer’s refinement process. Action arguments have been abbreviated. [1]
\label{fig:figure4}}
\end{figure}

This figure (Fig. \ref{fig:figure4}), included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.  
The subfigures in this diagram explain on a high level the different steps the interface layer takes when solving a problem.  
The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.  
Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.  
There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.  
This triggers the behavior discussed earlier, where the state is updated for the task planner.  
Subfigure e shows the new task plan after replanning occurs.  
After this, the interface layer will repeat the process of attempting to refine this new plan.  
Subfigure f shows an alternative option, where the blocking object is determined to be the table, which is not movable.  
Then, the state is updated as before and the task planner is called, but no solution is found, so backtracking occurs.

@@

\begin{figure}[t]
	\centering
	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm1}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
	\caption{Taken from[1]\label{fig:algorithms}}
\end{figure}

@@

The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

@@

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|}
\hline
Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
Horizontal Line & 3 & ? & ? & ? & ?\\
& 5 & ? & ? & ? & ?\\
& 7 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 11 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
\hline
Vertical lLne & 3 & ? & ? & ? & ?\\
& 5 & ? & ? & ? & ?\\
& 7 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 11 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\ 
\hline
X & 5 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
& 17 & ? & ? & ? & ?\\
& 21 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\ 
\hline
Cross & 5 & ? & ? & ? & ?\\
& 9 & ? & ? & ? & ?\\
& 13 & ? & ? & ? & ?\\
& 17 & ? & ? & ? & ?\\
& 21 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\ 
\hline
Square & 9 & ? & ? & ? & ?\\
& 25 & ? & ? & ? & ?\\
& 49 & ? & ? & ? & ?\\
& 81 & ? & ? & ? & ?\\
& 121 & ? & ? & ? & ?\\
& 169 & ? & ? & ? & ?\\ 
\hline
